---
title: 'Personal branding'
author: "Steph Locke (@SteffLocke)"
date: '`r Sys.Date()`'
output:
  stephStyle::stephRevealSlideStyle
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r autodoc, child='../../generics/AboutMe.Rmd', eval=TRUE}
```

# My Co-stars  {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obileia-costar.jpg"}

# What's motivating you?  {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obileia-sleep.jpg"}

# This isn't "being evil"  {data-background="https://github.com/stephlocke/lazyCDN/raw/master/leia-darkside.jpg"}

# What are your priorities? {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obi-grassisgreener.jpg"}

# What do you have passion for? {data-background="https://github.com/stephlocke/lazyCDN/raw/master/leia-provocative.jpg"}

# What are your goals? {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obi-looktothefuture.jpg"}

# Own yourself {data-background="https://github.com/stephlocke/lazyCDN/raw/master/leia-whatyoutalkingabout.jpg"}

# Boxes {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obi-box.jpg"}

# Work hard {data-background="https://github.com/stephlocke/lazyCDN/raw/master/leia-working.jpg"}

# Work some more! {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obi-working.jpg"}

# Look the part {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obi-lookthepart.jpg"}

# Respect other people {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obileia-respectspace.jpg"}

#Wrapup
## Wrapup
- Thank you!
- Questions?
- Get the slides from [stephlocke.info/Rtraining](http://stephlocke.info/Rtraining)
- Follow up [T: SteffLocke](https://twitter.com/stefflocke)
