---
title: 'The You in Community'
author: "Steph Locke (@SteffLocke)"
date: '`r Sys.Date()`'
output:
  stephStyle::stephRevealSlideStyle
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r autodoc, child='../../generics/AboutMe.Rmd', eval=TRUE}
```

## Live insight

> [bit.ly/youcommunity](https://bit.ly/youcommunity)


# What's this fluffy stuff? {data-background="https://github.com/stephlocke/lazyCDN/raw/master/leia-whatyoutalkingabout.jpg"}

# What motivates you?  {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obileia-payattention.jpg"}

# Who is your community? {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obileia-team.jpg"}

# Where do you fit? {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obi-box.jpg"}

# What are your other hobbies? {data-background="https://github.com/stephlocke/lazyCDN/raw/master/leia-angel.jpg"}

# ... {data-background="https://github.com/stephlocke/lazyCDN/raw/master/obileia-sleep2.jpg"}
## Communities and opportunities
- Friends & family
- Your organisation
- [Local R community](https://jumpingrivers.github.io/meetingsR/r-user-groups.html#south-africa)
- National R community - next year's SA satRday?
- Global R community

## Goodbye
- Thank you!
- Follow up [T: SteffLocke](https://twitter.com/stefflocke)
