---
title: 'shiny: repoRting'
author: "Steph Locke"
date: "`r Sys.Date()`"
output:
  Rtraining::stephSlideStyle
---

## Shiny
 - R
 - An interactive report framework
 - An open source package
 - Uses "modern web standards" like bootstrap under the hood 

## Examples
 - [Winston Chang Activity Dashboard](https://winston.shinyapps.io/activity-dashboard/)
 - [Movie explorer](http://shiny.rstudio.com/gallery/movie-explorer.html)

## Code example
```{r, eval=FALSE}
library(shiny)

shinyAppDir(
  system.file("examples/06_tabsets", 
              package="shiny")
)
```
 
## Pros & Cons
Pros | Cons
--------|--------
Free(mium) | Linux
Modern | != LDAP auth (free version)
Extensible | Fast pace of change
Solid SDLC | Code

## How do you build an app?
```{r, eval=FALSE}
shinyApp(
    ui      = fluidPage(),
  , server  = function(input,
                       output) {}
  , options = defaultdisplay
)
```

## DEMO

## How do you do the infrastructure?
Create an ubuntu VM, run the following commands

 - `sudo apt-get update`
 - `sudo apt-get install r-base`
 - `sudo su - -c "R -e \"install.packages('shiny', repos='http://cran.rstudio.com/')\""`
 - `sudo apt-get install gdebi-core`
 - `wget http://download3.rstudio.org/ubuntu-12.04/x86_64/shiny-server-1.3.0.403-amd64.deb`
 - `sudo gdebi shiny-server-1.3.0.403-amd64.deb`
 - `sudo nano /etc/shiny-server/shiny-server.conf`
 - `sudo restart shiny-server`

## DEMO

## How do you deploy apps?
### On-site
 1. [winSCP](http://winscp.net/eng/index.php)
 2. `git clone`
 
### shinyApps.io
 1. `shinyapps::deployApp()`

## DEMO
`git clone https://github.com/rstudio/shiny-examples`

## About Me
```{r autodoc, child='../../generics/AboutMe.Rmd', eval=TRUE}
```