---
title: 'Shiny: dashboards in R'
author: "Steph Locke (@SteffLocke)"
date: '`r Sys.Date()`'
output:
  Rtraining::stephSlideStyle
runtime: shiny
---

## Objective
Learn what the heck shiny is and how you use it!

<!--
## FundaRmentals
```{r,echo=TRUE}
# variable assignment
a <- 1
a
# functions
paste0(c("SQL","Star "),c("Bits","Wars"))
```

----
```{r,echo=TRUE}
# table
b <- data.frame(a,c=1:5,l=letters[5:1])
b
```
-->

## What's Shiny?
- An interactive report framework
- An R package that is available free (as is the server edition)
- Uses "modern web standards" like bootstrap under the hood 

## Quick example
```{r, echo = FALSE}
library(data.table)
library(shiny)
defaultdisplay<-list(
    width="100%", height="75%"
  )
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options = defaultdisplay
)
```

## Complex example
[Teaching stats with shiny](https://demo1.mango-solutions.com/shiny/ms/ah/)

## Complex example
[Board pack](https://github.com/stephlocke/Rtraining/tree/master/inst/applications/boardpack2)
<!--
## Why shiny, not PowerBI?
>- Firstly, PowerBI is amazeballs
>- It's excellent at allowing easy consumption
>- It does not however facilitate a workflow
>- Shiny does the dashboarding stuff + processing
-->

# Shiny structure
## Contents | Typical
A shiny application report consists of two functions[^1]

- `shinyServer()`
- `shinyUI()`

One says what to execute and the other states how to present it the results.

[^1]: Don't actually need to use these anymore

## Contents | "Lite"
```{r}
defaultdisplay<-list(width="100%", height="75%")

shinyApp(
    ui      = fluidPage()
  , server  = function(input, output) {}
  , options = defaultdisplay
)
```


## Files
You typically split into two files:  

- server.R containing `shinyServer()`
- ui.R containing `shinyUI()`

This can then be run with `runApp()`

You can do a single file example `app.R` which contains both functions but this is typically better for very short apps.

## Front-end layout

```{r, echo=FALSE}
lsp <- function(package, all.names = FALSE, pattern,...) 
{
  package <- deparse(substitute(package))
  ls(
      pos = paste("package", package, sep = ":"), 
      all.names = all.names, 
      pattern = pattern
  )
}
pages<-lsp(shiny,pattern = "Page")
pages<-pages[-grep(pattern ="^update|Handler$",pages)]
knitr::kable(data.table(`Page Types`=pages,` `=""))
```

# Some basic objects
## List of (standard) input types
```{r, echo=FALSE}
inputs<-lsp(shiny,pattern = "Input")
inputs<-inputs[-grep(pattern ="^update|Handler$",inputs)]
knitr::kable(data.table(`Input controls p1`=inputs[1:6],
           `Input controls p2`=c(inputs[7:11],"")
))
```

## List of (standard) output types
```{r, echo=FALSE}
outputs<-lsp(shiny,pattern = "Output")
knitr::kable(data.table(`Output controls p1`=outputs[1:4],
           `Output controls p2`=outputs[5:8]
))
```

## Dates
```{r}
shinyApp(
  ui = fluidPage(dateInput("datePicker"
                , "Pick a date:"
                , format="dd/mm/yy")),
  server = function(input, output) {}
  ,options = defaultdisplay
)
```

## Values | Sliders
```{r}
shinyApp(
  ui = fluidPage(sliderInput("vals"
              ,"Insert a number:"
              ,min=0 ,max=50 ,value=15
              ,ticks=FALSE))
  ,server = function(input, output) {}
  ,options = defaultdisplay
)
```


## Text | Paragraph
```{r}
shinyApp(
  ui = fluidPage(tags$textarea(id="charbox"
                    ,rows=3
                    ,cols=40
                    ,"Default value"))
  ,server = function(input, output) {}
  ,options = defaultdisplay
)
```


## Selectors 
```{r}
shinyApp(
  ui = fluidPage(selectInput("multiselect"
              ,"Pick favourites:"
              ,c("Green","Red","Blue")
              ,multiple=TRUE))
  ,server = function(input, output) {}
  ,options = defaultdisplay
)
```



## Text
```{r}
shinyApp(
  ui = fluidPage(textInput("char", "Insert text:") ,
                 textOutput("text")  ),
  server = function(input, output) {
    output$text <- renderText(input$char)
  }  ,options = defaultdisplay
)
```

## Let's make things short
```{r}
quickShiny <- function(uFUN,sFUN,s) {
  require(shiny)
  defaultdisplay <- list(width = "100%", height = "75%")
  shinyApp(
    ui = fluidPage(uFUN("a")),
    server = function(input, output) {
      output$a <- sFUN(s)
    },options = defaultdisplay
  )
}
```

## Interactive tables
```{r}
quickShiny(uFUN = DT::dataTableOutput,
           sFUN = DT::renderDataTable,
           s    = head(iris,5))
```

## Charts
```{r}
quickShiny(uFUN = plotOutput,
           sFUN = renderPlot,
           s    = pairs(iris[,1:3]))
```

# Some funky objects
## Leaflet maps
```{r}
library(leaflet)
quickShiny(uFUN = leafletOutput,
           sFUN = renderLeaflet,
           s    = leaflet() %>%  addTiles() )
```

## Dygraphs
```{r}
library(dygraphs)
quickShiny(uFUN = dygraphOutput,
           sFUN = renderDygraph,
           s    = dygraph(mdeaths))
```

## Graphs
```{r}
library(DiagrammeR)
quickShiny(uFUN = grVizOutput,
           sFUN = renderGrViz,
           s    = render_graph(create_random_graph(3,3)))
```

## Plot.ly
```{r}
library(plotly)
quickShiny(uFUN = plotlyOutput,
           sFUN = renderPlotly,
           s    = plot_ly(z = volcano, type = "surface"))
```

# Reactivity

## Simple
```{r}
uilist<-list(textInput("a","Text","Txt")
      ,textOutput("b"))
shinyApp(ui = fluidPage(uilist)
  ,server = function(input, output) {
    output$b <-renderText(paste0(input$a,"er"))
  },options = defaultdisplay
)
```

## DRY
```{r}
shinyApp(ui = fluidPage(uilist)
  ,server = function(input, output) {
    rand<-reactive({gen<-rpois(1,5)+1
                   paste0(gen,input$a)})
    output$b <-renderText(rand())
  },options = defaultdisplay
)
```

## Isolated
```{r}
uilist[[3]]<-actionButton("go","Go")
shinyApp(ui = fluidPage(uilist)
  ,server = function(input, output) {
    rand<-eventReactive(input$go
                  ,{gen<-rpois(1,5)+1
                   paste0(gen,input$a)})
    output$b <-renderText(rand())
  },options = defaultdisplay
)
```

# Styling
## CSS
- Shiny outputs html so you can write CSS that works with it
- Full list of CSS items doesn't exist, use F12 on chrome or check out selectorgadget via `rvest`
- Standard classes will work

## shinythemes
- Get a different look and feel with the package `shinythemes`
- Uses a number of bootstrap based themes
- Good-looking quickly, but of course not company branded
- View themes at [bootswatch.com](http://bootswatch.com/)

## shinydashboards
- A new dashboarding : [Shiny Dashboard](http://rstudio.github.io/shinydashboard/)
- Still immature but useful
- Excellent walkthrough on [Data Driven Security](http://datadrivensecurity.info/blog/posts/2015/Jan/building-security-dashboards-with-r-and-shiny-shinydashboard/)

# Infrastructure
## Ad-hoc shiny
- Rstudio (easiest) or just run directly
- Use `shiny::runApp()`
- Great for "expert" use

## Cloud
- [shinyApps.io](https://www.shinyapps.io/)
- Deploy with `shinyApps` package
- Free for light use 
- Extra management features at increased costs
- Great for hands-off management

## Central server
- shiny-server
- Runs on linux
- Free community edition
- Extra management features & LDAP auth in Pro Edition (but can roll your own)
- Great for sensitive and/or db-driven appplications

# Wrap up

## Conclusion
>- shiny is an easy framework
>- shiny is very extendable
>- shiny has a variety of deployment options

## Get the code
- Browse on github: [stephlocke/Rtraining](https://github.com/stephlocke/Rtraining/blob/master/inst/slidedecks/shiny/shinyDashboards.Rmd)
- Download **everything**: 
```r
if (!require(devtools)) install.packages("devtools")
devtools::install_github("stephlocke/Rtraining")
```

## Q & A

## Thank you
>- Attendees
>- Organisers and volunteers
<!-- >- Sponsors -->

## Recommended reading
- [Shiny site](http://shiny.rstudio.com/)
- A bit outdated but: [Web Application Development with R Using Shiny](http://www.amazon.co.uk/gp/product/B00G395OOY)
- [Reactivity Overview](http://shiny.rstudio.com/articles/reactivity-overview.html)
- [shiny for teaching maths](https://github.com/hadley/reactive-docs)
- [Show me Shiny!](http://www.showmeshiny.com/)
- [Deploying shiny apps](http://shiny.rstudio.com/tutorial/lesson7/)

```{r autodoc, child='../../generics/AboutMe.Rmd', eval=TRUE}
```



# The end!
