---
title: "R: from analysis to integration"
author: "Steph Locke"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    theme: readable
---
```{r setup, eval=TRUE, results='hide', echo=FALSE}
knitr::opts_knit$set(warning = FALSE, message= FALSE)
```

# Front Matter

<a href="#top">Back to top</a>

```{r autodoc, child='frontmatter/objective.Rmd', eval=TRUE}
```

```{r autodoc, child='frontmatter/aboutme.Rmd', eval=TRUE}
```

# R

<a href="#top">Back to top</a>

```{r autodoc, child='fundamentals/R.Rmd', eval=TRUE}
```

# Installation

<a href="#top">Back to top</a>

```{r autodoc, child='infrastructure/setting-up-a-windows-R-Machine.Rmd', eval=TRUE}
```

#  Syntax & structure

<a href="#top">Back to top</a>

```{r autodoc, child='fundamentals/syntax.Rmd', eval=TRUE}
```

#  Data types

<a href="#top">Back to top</a>

```{r autodoc, child='fundamentals/datatypes.Rmd', eval=TRUE}
```

#  IO

<a href="#top">Back to top</a>

```{r autodoc, child='fundamentals/io.Rmd', eval=TRUE}
```

#  Wrangling tables

<a href="#top">Back to top</a>

```{r autodoc, child='fundamentals/tablewrangling.Rmd', eval=TRUE}
```

#  Making charts

<a href="#top">Back to top</a>

```{r autodoc, child='dataviz/chartintro.Rmd', eval=TRUE}
```


#  Making documents

<a href="#top">Back to top</a>

```{r autodoc, child='documents/writingdocuments.Rmd', eval=TRUE}
```

#  Making reports

<a href="#top">Back to top</a>

```{r autodoc, child='documents/DashboardsHandout.Rmd', eval=TRUE}
```

#  Making diagrams

#  LaTeX

<a href="#top">Back to top</a>

```{r autodoc, child='documents/latex.Rmd', eval=TRUE}
```

#  Source control - theory

<a href="#top">Back to top</a>

```{r autodoc, child='development/sourcecontrol.Rmd', eval=TRUE}
```

# Source control - tfsR

<a href="#top">Back to top</a>

```{r autodoc, child='development/tfsR.Rmd', eval=TRUE}
```

<!--
# Source control - git2r

<a href="#top">Back to top</a>

```{r autodoc, child='development/git2r.Rmd', eval=TRUE}
```

-->

#  Testing
#  Package development
#  Continuous integration with Travis-CI

```{r autodoc, child='development/travisci.Rmd', eval=TRUE}
```

#  Linux basics
#  Installing Rstudio

#  Installing shiny-server
```{r autodoc, child='infrastructure/shiny-server build.Rmd', eval=TRUE}
```

#  AD authentication
