---
title: "R: from analysis to integration"
author: "Steph Locke"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    theme: united
---

# Front Matter
```{r autodoc, child='frontmatter/objective.Rmd', eval=TRUE}
```

```{r autodoc, child='frontmatter/aboutme.Rmd', eval=TRUE}
```

# R
```{r autodoc, child='../slidedecks/R basics/R.Rmd', eval=TRUE}
```

# Installation
```{r autodoc, child='infrastructure/setting-up-a-windows-R-Machine.Rmd', eval=TRUE}
```

#  Syntax & structure
```{r autodoc, child='fundamentals/syntax.Rmd', eval=TRUE}
```

#  Data types
```{r autodoc, child='fundamentals/datatypes.Rmd', eval=TRUE}
```

#  IO
```{r autodoc, child='fundamentals/io.Rmd', eval=TRUE}
```

#  Wrangling tables
```{r autodoc, child='fundamentals/tablewrangling.Rmd', eval=TRUE}
```

#  Making charts
#  Bonus round: magrittr & dplyr


#  Making documents
#  Making reports
#  Making diagrams
#  Bonus round: LaTeX

#  Source control
#  Testing
#  Package development
#  Bonus round: Continuous integration with Travis-CI

#  Linux basics
#  Installing Rstudio
#  Installing shiny-server
#  Bonus round: AD authentication
