## How to implement

### Ideal
- Write a package
- Add unit tests
- Use source control
- Use best of breed packages
- Do DataOps
- Deploy to right architecture for your business

## How to implement

### Quick & dirty
- Write some code as a function
- Use `AzureML` package to publish code

## How to implement - AzureML demo

### Setup

```{r echo=TRUE, eval=FALSE}
library("AzureML")
MLID<-"16ed88890b0644239ea800a90063bc0f"
AuthToken<-"e1e2d4f99b0041269c6435c0c6ccb07d"
```

## How to implement - AzureML demo

### Make a model

```{r echo=TRUE, eval=FALSE}
myLM<-lm(data = iris,Sepal.Length~Sepal.Width,model = FALSE)
adhocPred<-predict(myLM,newdata = data.frame(Sepal.Width=5.7))
adhocPred
```

## How to implement - AzureML demo

### Make a predict function
```{r echo=TRUE, eval=FALSE}
myPrediction<-function(SW=0){
  # You would store coeficients
  # In place of modelling every time!
  myCoefsLM<-coef(lm(data = iris,
           Sepal.Length~Sepal.Width,
           model = FALSE))
  myCoefScores<-crossprod(myCoefsLM,c(1,SW))
  return(sum(myCoefScores))
  
}
```

## How to implement - AzureML demo

### Publish a predict function
```{r echo=TRUE, eval=FALSE}
response <- publishWebService("myPrediction", "myPredictionOnline",                              list("SW"="float"), list("r"="float"), 
                              MLID, AuthToken)
```


## How to implement - AzureML demo

### Use a published functions
```{r echo=TRUE, eval=FALSE}
webservices <- getWebServices(MLID, AuthToken)
endpoints <- getEndpoints(MLID, AuthToken, webservices[[1]]$Id)
response <- consumeLists(endpoints[[1]]$PrimaryKey, endpoints[[1]]$ApiLocation, 
                         list("SW"=9))

response
```
