---
title: "Intro to R"
author: "Steph Locke"
date: "@ London Business Analytics Group"
output:
  ioslides_presentation:
    css: Look.css
---

```{r autodoc, child='Objective.Rmd', eval=TRUE}
```

```{r autodoc, child='AboutMe.Rmd', eval=TRUE}
```

```{r autodoc, child='Scenario.Rmd', eval=TRUE}
```

## Step 1: Google "What is R?"
I [Google](http://lmgtfy.com/?q=what+is+r) frantically and find out...

- R (birthed out of S) has been around for ages
- Has [massively increased in popularity](http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html)
- Lots of big players like SAP, TIBCO, and Oracle have implemented it
- It's statistician heaven!
- It produces very pretty charts
- Huh, you can make [XKCD cartoons in it](http://stackoverflow.com/questions/12675147/how-can-we-make-xkcd-style-graphs-in-r)?

Eep, but I'm not a stats bod or a programmer, what will I do? Do my usual stuff, but swisher!

## Step 2: Get R installed

- Install R from [r-project.org](http://www.r-project.org/) yourself
- Install Rstudio via [Rstudio.com](http://www.rstudio.com) if possible
- Use R to nab some useful packages

------
```{r autodoc, child='Packages.Rmd', eval=TRUE}
```


```{r autodoc, child='Database.Rmd', eval=TRUE}
```

```{r autodoc, child='Dataset.Rmd', eval=TRUE}
```

```{r autodoc, child='Summarise.Rmd', eval=TRUE}
```

## Step 6: Make charts of data

## Step 7: Produce presentation

## Step 8: Produce report

## Conclusion

## Where next?
