---
title: 'Microsoft SQL Server and R Services'
author: "Steph Locke (@SteffLocke)"
date: '`r Sys.Date()`'
output:
  stephStyle::stephRevealSlideStyle
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r autodoc, child='../../generics/AboutMe.Rmd', eval=TRUE}
```

# SQL Server

## Overview
- RDBMS
- Use on physical or virtual machines

## Key things to manage
- Data
- Code
- Permissions
- Licences

## Next steps
- [Books Online](https://msdn.microsoft.com/en-us/library/ms130214.aspx)
- [SQL Server Central](http://www.sqlservercentral.com/)


# R

## Overview
> R is an integrated suite of software facilities for data manipulation, calculation and graphical display

- Open source
- In-memory & single-core (by default)
- Multi-platform
- Extensible environment
- Delivered by the [R Foundation](https://www.r-project.org/foundation/), supported by the [R Consortium](https://www.r-consortium.org/), grown by R developers 
- [r-project.org](http://www.r-project.org/)

## What's it look like?
```{r}
ggplot2::qplot(mpg, wt, data = mtcars, colour = cyl)
```

## Versions
- ["Standard" R](https://r-project.org)
- [Microsoft R Open](https://mran.revolutionanalytics.com/download/)
- [Microsoft R Server](https://msdn.microsoft.com/en-us/library/mt674876.aspx)
- [TERR](https://docs.tibco.com/products/tibco-enterprise-runtime-for-r)
- [Oracle R](http://www.oracle.com/technetwork/database/database-technologies/r/r-distribution/overview/index.html)

## Key things to manage
- Packages
- RAM
- Code

## Next steps
- [Learn R](https://datacamp.com)
- [Check out some of my other intros to R](http://stephlocke.info/Rtraining)

# SQL Server + R Services

## Overview
- Call R through SQL Server

## What's it look like?
```
EXECUTE   sp_execute_external_script
                @language = N'R'
              , @script = N'OutputDataSet <- df<-as.data.frame(installed.packages()[,1])'
              , @input_data_1 = N'SELECT 1 as Col'
 WITH RESULT SETS ((col varchar(50) not null))        
```

## 2016 Editions
- Express - R Open or base R
- Standard - R Open or base R
- Enterprise - R Server

[SQL Server feature comparison](https://www.microsoft.com/en-ie/sql-server/sql-server-editions)


## Key things to manage
- RAM & CPU
- Licenses vs Server resources
- Permissions
- Code

## Next steps
- [Tomaz Kastrun blog](https://tomaztsql.wordpress.com/)
- [BOL](https://msdn.microsoft.com/en-us/library/mt604845.aspx)

# Deploying SQL Server & R Services

## Azure is your friend
- Automatable
- Disposable
- Scalable

## ARM templates
- JSON specification of resources
- Paramaterised for reuse
- Downloadable
- Deploy in many different languages

## PowerShell
- Azure modules
- Use ARM templates
- Used in Azure Automation

## Demo
[Github](https://github.com/stephlocke/SQLServerVM-tidyverse)

## Next steps
- [Authoring ARM templates](https://azure.microsoft.com/en-gb/documentation/articles/resource-group-authoring-templates/)
- [PowerShell basics](https://msdn.microsoft.com/en-us/powershell/scripting/getting-started/fundamental/windows-powershell-basics)
- [Azure overview](https://azure.microsoft.com/en-gb/overview/what-is-azure/)

# Other Microsoft & R things

## Azure ML
- GUI data science
- R & Python
- Notebooks
- Code deployment potential
- Easy webservices

## R in PowerBI
- Interactive reports
- R data source
- R graphics

# Wrapup
## Wrapup
- Thank you
- Check out the Next Steps
- Get in touch! [T: SteffLocke](https://twitter.com/stefflocke)