---
title: 'Shiny: dashboards in R'
author: "Steph Locke (@SteffLocke)"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: journal
---

## What's Shiny?
- An interactive report framework
- An R package that is available free (as is the server edition)
- Uses "modern web standards" like bootstrap under the hood 
- Cross-browser/Cross-device compatibility, out of box!

## Quick example
```{r, eval=FALSE, echo = TRUE}
library(data.table)
library(shiny)
defaultdisplay<-list(
    width="100%", height="75%"
  )
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options = defaultdisplay
)
```

## Shiny structure
### Typical Contents
A shiny application report consists of two functions:

- `shinyServer()`
- `shinyUI()`

One says what to execute and the other states how to present it. Do all data manipulation, chart production in `shinyServer()`

### "Lite" Contents
```{r, eval=FALSE}
defaultdisplay<-list(width="100%", height="75%")

shinyApp(
    ui      = fluidPage(),
  , server  = function(input, output) {}
  , options = defaultdisplay
)
```


## Files
You typically split into two files:  

- server.R containing `shinyServer()`
- ui.R containing `shinyUI()`

This can then be run with `runApp()`

You can do a single file example `app.R` which contains both functions but this is typically better for very short apps.

## Front-end layout
Use these just inside `shinyUI()` to produce a layout

```{r, echo=FALSE}
library(shiny)
library(data.table)
lsp <- function(package, all.names = FALSE, pattern) 
{
  package <- deparse(substitute(package))
  ls(
      pos = paste("package", package, sep = ":"), 
      all.names = all.names, 
      pattern = pattern
  )
}
data.table(`Page Types`=lsp(shiny,pattern = "Page"))
```

## Typical Inputs
### Dates
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(dateInput("datePicker", "Pick a date:", 
                           format="dd/mm/yy"),
                 dateRangeInput("dateRange", "Pick dates:", 
                                start=Sys.Date(), 
                                end=Sys.Date() ) ),
  server = function(input, output) {}
  ,options = defaultdisplay
)
```

### Values 
Basic
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(numericInput("vals", "Insert a number:", 
                              value=15, min=10)  ),
  server = function(input, output) {}
  ,options = defaultdisplay
)
```

Sliders

```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(sliderInput("vals", "Insert a number:", 
                             min=0, max=50, value=15)  ),
  server = function(input, output) {}
  ,options = defaultdisplay
)
```

### Text
A single line
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(textInput("char", "Insert text:")  ),
  server = function(input, output) {}
  ,options = defaultdisplay
)
```

A paragraph
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(tags$textarea(id="charbox", rows=3, 
                               cols=40, "Default value")  ),
  server = function(input, output) {}
  ,options = defaultdisplay
)
```


### Selectors 
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(selectInput("multiselect", "Pick favourites:",
                             c("Green","Red","Blue"),
                             multiple=TRUE)  ),
  server = function(input, output) {}
  ,options = defaultdisplay
)
```

## List of input types

```{r, echo=FALSE}
data.table(`Input controls`=lsp(shiny,pattern = "Input"))
```


## Typical Outputs
### Input values
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(textInput("char", "Insert text:") ,
                 textOutput("text")  ),
  server = function(input, output) {
    output$text <- renderText(input$char)
  }  ,options = defaultdisplay
)
```

### Basic tables
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(tableOutput("basictable")  ),
  server = function(input, output) {
    output$basictable <- renderTable(head(iris,5))
  }  ,options = defaultdisplay
)
```

### Interactive tables
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(dataTableOutput("datatable")  ),
  server = function(input, output) {
    output$datatable <- renderDataTable(head(iris,5))
  }  ,options = defaultdisplay
)
```

### Charts
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(plotOutput("chart")  ),
  server = function(input, output) {
    output$chart <- renderPlot(pairs(iris))
  }  ,options = defaultdisplay
)
```


## Reactivity
### Simple reactivity
- Make functions that process inputs only when they change
```{r, eval=FALSE}
a <- reactive({input$a})
a
```
- Use these reactive functions in downstream server items for DRY & to reduce processing effort

### An Example
```{r, eval=FALSE}
shinyApp(
  ui = fluidPage(textInput("char", "Insert text:") ,
                 textOutput("textA"),textOutput("textB") ),
  server = function(input, output) {
    char<-reactive({rep(input$char,5)})
    output$textA <- renderText(paste(char(),collapse="+"))
    output$textB <- renderText(paste(char(),collapse="-"))
  }
  ,options = defaultdisplay
)
```

## Styling
### shinythemes
- Get a different look and feel with the package `shinythemes`
- Uses a number of bootstrap based themes
- Good-looking quickly, but of course not company branded
- View themes at [bootswatch.com](http://bootswatch.com/)

### CSS
- Shiny outputs html so you can write CSS that works with it
- Full list of CSS items doesn't exist, use F12 on chrome or check out selectorgadget via `rvest`
- Simple stuff like body, h1 will all work

### shinydashboards
- Makers of shiny working on a framework: [Shiny Dashboard](http://rstudio.github.io/shinydashboard/)
- A new dashboarding framework - still immature but useful
- Excellent walkthrough on [Data Driven Security](http://datadrivensecurity.info/blog/posts/2015/Jan/building-security-dashboards-with-r-and-shiny-shinydashboard/)

## Infrastructure
### Ad-hoc shiny
- Rstudio (easiest) or just run directly
- Use `shiny::runApp()`
- Great for "expert" use

### Cloud
- [shinyApps.io](https://www.shinyapps.io/)
- Deploy with `shinyApps` package
- Free for light use 
- Extra management features at increased costs
- Great for hands-off management

### Central server
- shiny-server
- Runs on linux
- Free community edition
- Extra management features & LDAP auth in Pro Edition (but can roll your own)
- Great for sensitive and/or db-driven appplications

### Recommended reading
- [Shiny site](http://shiny.rstudio.com/)
- A bit outdated but: [Web Application Development with R Using Shiny](http://www.amazon.co.uk/gp/product/B00G395OOY)
- [Reactivity Overview](http://shiny.rstudio.com/articles/reactivity-overview.html)
- [shiny for teaching maths](https://github.com/hadley/reactive-docs)
- [Show me Shiny!](http://www.showmeshiny.com/)
- [Deploying shiny apps](http://shiny.rstudio.com/tutorial/lesson7/)
