## Basic analysis - data.table & ggplot2 {#basicanalysis}
data.table and ggplot2 are probably the two most useful packages in R!

### data.table
* data.table enhances data.frames (tables) to give you grouping, filtering, joins, aggregations and column names. 
* It's quite SQL-like and is designed to be **very fast**.

### ggplot2
* ggplot2 implements a grammar of graphics (gg)
* Simple, consistent functions to build charts

## data.table

## Grab some data {.smaller}
```{r, echo=TRUE, eval=TRUE}
# SQL statement
sales <- sqlQuery(azure, "
SELECT 
soh.OrderDate,
t.Name as Territory,
cr.countryregioncode as Code,
cr.Name as Region,
sum(TotalDue) as Value,
count(*) as Volume
FROM [Sales].[SalesOrderHeader] soh
INNER JOIN [Sales].[SalesTerritory] t 
          on t.territoryid=soh.territoryid
INNER JOIN [Person].[CountryRegion] cr 
          on cr.countryregioncode=t.countryregioncode
WHERE  soh.OrderDate < '2008-07-01'
GROUP BY soh.OrderDate,
t.Name ,
cr.Name,
cr.countryregioncode")
```

```{r, echo=FALSE, eval=TRUE, results='hide'}
suppressPackageStartupMessages({
  library(knitr)
library(zoo)
library(knitr)
library(data.table)
library(scales)
})
options("scipen"=100, "digits"=4)
# This is a temporary fix for an issue in latest data.table release- it'll work for historic versions too
# See https://github.com/Rdatatable/data.table/issues/809
kable<-function(...){knitr::kable(as.data.frame(...))}
```

## Simples
```{r, echo=TRUE, eval=TRUE}
# Convert to data.table
sales<-data.table(sales)

# Basic GROUP BY aggregation - returns count by region
sales[,.N,by=Region]
```

## Row extraction
```{r, echo=TRUE, eval=TRUE, results='asis'}
# .SD returns the subset of rows and is filtered by which.max
kable(sales[,.SD[which.max(Value)],by=Region])
```

## Aggregation
```{r, echo=TRUE, eval=TRUE, results='asis'}
# ORDER, multiple aggregations, and aliasing
kable(sales[order(OrderDate),.(Value=sum(Value),Volume=sum(Volume))
            ,by=.(Year=year(OrderDate))])
```

## Joins {.smaller}
```{r, echo=TRUE, eval=TRUE, results='asis'}
salesbyyear<-sales[,.(AnnualValue=sum(Value),AnnualVolume=sum(Volume))
                   ,keyby=.(Year=year(OrderDate))]
salesbyregion<-sales[,.(Value=sum(Value),Volume=sum(Volume))
                   ,by=.(Region,Year=year(OrderDate))]

setkey(salesbyregion,Year) #PK assignment for non-unique column
kable(salesbyyear[salesbyregion[Region=="United Kingdom"],
            .(Proportion=percent(Volume/AnnualVolume)),by=.EACHI])

```

## ggplot2

## Quick chart {.smaller}
```{r, echo=TRUE, eval=TRUE}
library(ggplot2) # Activate ggplot2

# Quick plot (qplot)
qplot(year(OrderDate), Value,fill=Region,
      data=sales[order(Region)],geom="bar",stat="identity")
```

## Chart anatomy {.smaller}
```{r, echo=TRUE, eval=TRUE}
# Chart backbone
ggplot(data=sales[order(Region)],aes(x=year(OrderDate),y=Value,fill=Region))+
  geom_bar(stat="identity")+#bar chart type, identity uses contents not count
  scale_fill_brewer(type="qual")+ #themeing
  theme_minimal()
```

## Making a trellis {.smaller}
```{r, echo=TRUE, eval=TRUE}
ggplot(data=sales,aes(x=year(OrderDate),y=Value,fill=Region))+
  geom_bar(stat="identity")+
  facet_grid(.~Region)+  # Trellis command
  theme(legend.position="none",axis.text.x=element_text(angle=45))  
```

## Formatting {.smaller}
```{r, echo=TRUE, eval=TRUE}
ggplot(data=sales,aes(x=year(OrderDate),y=Value/1000000,fill=Region))+
  geom_bar(stat="identity")+   facet_grid(.~Region)+
  theme_minimal(base_size = 10) +
  theme(legend.position="none",axis.text.x=element_text(angle=45,hjust=1))+
  scale_y_continuous(label=dollar)+
  labs(x="Year",y="Value ($m)")
```
