---
title: "An introduction to R"
author: "Steph Locke (@SteffLocke)"
date: "SQLRelay"
output:
  ioslides_presentation:
    fig_height: 4
    fig_width: 6.5
---
## Agenda
- Introductory stuff
- Connecting to SQL Server 
- Basic analysis with data.table and ggplot2
- Building interactive reports
- Dynamically built documents
- Q&A & Conclusion

```{r autodoc, child='Introduction.Rmd', eval=TRUE}
```

```{r autodoc, child='AboutStef.Rmd', eval=TRUE}
```

```{r autodoc, child='AboutR.Rmd', eval=TRUE}
``` 

```{r autodoc, child='InstallR.Rmd', eval=TRUE}
``` 

```{r autodoc, child='SQLServer.Rmd', eval=TRUE}
``` 

```{r autodoc, child='BasicAnalysis.Rmd', eval=TRUE}
``` 

```{r autodoc, child='InteractiveReports.Rmd', eval=TRUE}
``` 

```{r autodoc, child='Documentation.Rmd', eval=TRUE}
``` 

```{r autodoc, child='MoreInfo.Rmd', eval=TRUE}
``` 

## Q&A {#conc}

## Conclusion
R is a great language that has a wide array of uses. This session covered some of the basics of data manipulation to get you "walking" quickly.

### Follow up
This presentation is available at http://rpubs.com/stephlocke/sqlrelay and the source code is on https://github.com/stephlocke/Rintro

- http://twitter.com/stefflocke
- http://uk.linkedin.com/in/stephanielocke