## Working with SQL Server {#sql}
First things first - get a SQL Server driver

Secondly - install the RODBC package for R and activate it
```{r, echo=TRUE, eval=TRUE}
install.packages("RODBC",repos="http://cran.ma.imperial.ac.uk/")
# Activate the ODBC package for use
library("RODBC")

```

----

Thirdly - connect and grab some data!

```{r, echo=TRUE, eval=TRUE}
# Connection courtesy of Redgate bit.ly/1jrl7V6

# Build a connection to the DB for reuse
azure <- odbcDriverConnect(
          "Driver={SQL Server Native Client 11.0};
          Server=mhknbn2kdz.database.windows.net;
          Database=AdventureWorks2012;
          Uid=sqlfamily;
          Pwd=sqlf@m1ly;")

# Store simple SELECT statement results
person <- sqlQuery(azure, 
         "SELECT TOP 5 * FROM [Person].[Person]")
```

----

Inline example of dynamic results: `r nrow(person)` records returned on previous page and details below

```{r, echo=TRUE, eval=TRUE}
#Show results
person
```

----

### Notes on connecting
- You can use DSNs, I've just done it explicitly for proof
- You can use the `TrustedConnection` property for AD authenticating logins
- You can write functions to hide the different steps to make it quicker in future
- Multiple statements can be troublesome - try to keep to just one
