---
title: 'Infrastructure for R peeps'
author: "Steph Locke (@SteffLocke)"
date: '`r Sys.Date()`'
output:
  Rtraining::stephRevealSlideStyle
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Poll
[http://dpll.co/17175e5](http://dpll.co/17175e5)

```{r autodoc, child='../../generics/AboutMe.Rmd', eval=TRUE}
```

# Agenda
## Agenda
- Fundamentals
- Windows
- Linux
- Mac OS
- Containers


# Fundamentals

## Hard-won lessons
- Do work today so tomorrow's work is new and interesting
- You're only as good as your last restore
- Use the VMs & the cloud
- Never use sa

## Networks
- Access
    + Names
    + IPs
    + Device addresses
- Restricting access
    + Firewalls
- Safety
    + Ports
    + Whitelisting

## Storage
- Access
    + Persistence
    + Users
    + Metadata
- Restricting access
    + Permissions
- Safety
    + Role Based Access

## OS
- Access
    + Authentication systems
- Restricting access
    + Permissions
- Safety
    + User hygeine

# Windows specifics

## PowerShell
The language for working with all things Microsoft these days.

>- Also works on Linux

```powershell
Get-ChildItem | 
  Where Name -notlike "*.tar.gz" |
    Export-Csv "filelist.csv"

Import-Csv "filelist.csv"
```

## Networks
[Howtogeek.com](http://www.howtogeek.com/school/windows-network-sharing/)

## Storage
- Case insensitive
- Permissions inherit from parent object by default


## OS Variants
- Windows 10 - not a server
- Windows server YYYY - GUI
- Windows Nano - Headless

## Follow on
- [TechNet library](https://technet.microsoft.com/en-us/library/bb625087.aspx)
- [Microsoft Virtual Academy](https://mva.microsoft.com/product-training/windows-server#!jobf=IT%20Professional&lang=1033)


# Linux

## Bash
## Networks
## Storage
## Software
## Follow on


# Mac OS

## Mac OS
Tough! I don't know anything about this!

```{r autodoc, child='subDocs/Docker.Rmd', eval=TRUE}
```

# Wrap up
## Wrap up
- More questions during the break
- Get the slides: [bit.ly/infRastructure](http://bit.ly/infRastructure)
- Keep in touch: @SteffLocke