---
title: 'Reproducible R docs in GitHub'
author: "Steph Locke (@SteffLocke)"
date: '`r Sys.Date()`'
output:
  stephStyle::stephRevealSlideStyle
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r autodoc, child='../../generics/AboutMe.Rmd', eval=TRUE}
```

# Agenda
## Agenda
- R Docs
- Github pages
- Travis-CI
- Package docs
- Studies
- Presentations
- Books
- Blogs

# R Docs
## What
- Anything that you can generate with R!

## Why
- Version control
- Hosting
- Validation
- Automation

## How
- Use processes to build docs and deploy them somewhere
- Travis-CI is a handy way to deploy to github

## When
- Ideally every commit!

## Where
- Github is free hosting
- Can also work elsewhere

## Examples
- Vignettes: [tfsR](http://stephlocke.info/tfsR/)
- Package docs: [sparklyr](http://spark.rstudio.com/)
- Documents: [ISC Conference Management proposal](https://hturner.github.io/conf-management-proposal/conference-management-proposal.html)
- Presentations: [Rtraining/reproducibledocs](http://stephlocke.info/Rtraining/reproducibledocs.html)
- Books: [R for data science](http://r4ds.had.co.nz/)
- Blogs: [Kevin Wong's blog](http://kevinfw.com/)

# Github Pages
## Deployment locations
- **master**: The primary branch
- **gh-pages**: A dedicated branch of the project
- **/docs**: A directory in your master branch

## DNS
- **A Records** Associate a whole domain with location
- **CNAME** Associate a subdomain with location
- Directory structure - anything "below" a domain / subdomain

> satrdays.org = Domain
>
> captetown.satrdays.org = Subdomain
>
> satrdays.org/satRdays-devsite = Directory

## X.github.io
A project with your username that serves as the entrypoint to all your github hosted stuff

- This top-level site's files must be in master branch
- Associate a domain to this to yield a directory structure

# Travis-CI
## Travis-CI 
- **Continuous Integration** Testing in a clean environment
- **Build artifacts** Items produced by the CI build process

There are other alternative CI systems, esp. if you need to work with private repos

## R language
Your `.travis.yml`

```
language: r
```

- Travis CI [R docs](https://docs.travis-ci.com/user/languages/r/)

## Custom actions
There are triggers which allow you perform actions at different points in the process. Can run any bash command here, including calling R!

```yaml
after_success:
  - R CMD build .
  - chmod 755 .push_gh_pages.sh
  - ./.push_gh_pages.sh
```
# Package Docs
## Vignettes
- Vignettes get produced in the build process for your package
- Extract them for the build directory and deploy them somewhere

## ./.push_gh_pages.sh
```bash
#!/bin/bash
GH_REPO="@github.com/$TRAVIS_REPO_SLUG.git"
FULL_REPO="https://$GH_TOKEN$GH_REPO"

git config --global user.name "stephs-travis"
git config --global user.email "steph@travis.ci"

for files in '*.tar.gz'; do
        tar xfz $files
done

git clone $FULL_REPO out --branch gh-pages

for files in 'inst/doc/*.html'; do
        cp $files out
done

cd out
git add .
git commit -m "$TRAVIS_COMMIT"
git push --quiet $FULL_REPO
```

## pkgdown
A package to generate package websites!

 - Can produce files locally
 - Can run process in Travis

[pkgdown](http://hadley.github.io/pkgdown)

# Studies
## R markdown
- Make any R markdown project into a package by simply having a DESCRIPTION file
- Have R scripts that knit your reports

## ghgenerate.r
```r
library(rmarkdown)
reports <- list.files(
  "inst/reports", pattern = "*.Rmd"
  , recursive = TRUE ,full.names = TRUE
``)
for (f in reports) render(f,output_dir = "out"
          ,output_format = html_document())
render("inst/index.Rmd", output_dir = "out"
      ,intermediates_dir = "out")
```

## ./.push_gh_pages.sh
```bash
#!/bin/bash
FULL_REPO="https://$GH_TOKEN$@github.com/$TRAVIS_REPO_SLUG.git"

git clone $FULL_REPO out --branch gh-pages
cd out
git config user.name "stephs-travis"
git config user.email "steph@travis.ci"

cd ..
R CMD BATCH '../Rtraining/ghgenerate.R'

cp ghgenerate.Rout out
cd out

git add .
git commit -m "$TRAVIS_COMMIT"
git push --quiet $FULL_REPO
```

# Presentations
## reveal.js
Using [revealjs](cran.r-project.org/package=revealjs), produce HTML sliides like these!

There are others coming along like [xaringan](https://cran.r-project.org/package=xaringan
) too

## ghgenerate.r
```r
library(rmarkdown)
reports <- list.files(
  "inst/slidedecks", pattern = "*.Rmd"
  , recursive = TRUE ,full.names = TRUE
``)
for (f in slidedecks) render(f,output_dir = "out"
          ,output_format = stephStyle::stephRevealSlideStyle())
render("inst/index.Rmd", output_dir = "out"
      ,intermediates_dir = "out")
```

# Books
## bookdown
[MeetingsR](https://github.com/jumpingrivers/meetingsR) is a neat example of a project using [bookdown](https://cran.r-project.org/package=bookdown).

Get in-depth with Yi Hui's book [bookdown: Authoring Books and Technical Documents with R Markdown](https://bookdown.org/yihui/bookdown/)

## .travis.yml
```yaml
language: r
cache: packages

script:
  - make html

after_success:
  - test $TRAVIS_PULL_REQUEST == "false" && test $TRAVIS_BRANCH == "master" && bash deploy.sh
```

## Makefile
```yaml
html:
	Rscript -e 'bookdown::render_book("index.Rmd", output_format = "bookdown::gitbook", clean = FALSE)'
	cp -fvr css/style.css _book/
	cp -fvr _main.utf8.md _book/main.md

build:
	make html
	Rscript -e 'browseURL("_book/index.html")'
```
## deploy.sh
```bash
#!/bin/bash
FULL_REPO="https://$GH_TOKEN$@github.com/$TRAVIS_REPO_SLUG.git"

git clone $FULL_REPO book-output
cd book-output
git config user.name "stephs-travis"
git config user.email "steph@travis.ci"

cp -fvr ../_book/* docs/
cd docs
git add libs/; git add css/
git add *.json; git add *.html; git add main.md; git add style.css
cd ..
git commit -am "Travis: updating website (${TRAVIS_BUILD_NUMBER})"
git push origin master 2>err.txt
```

# Blogs
## blogdown
Uses Hugo (which I love) to build a static blog site with Rmarkdown posts

[blogdown](https://github.com/rstudio/blogdown)

## Deployment
- Local build & commit
- CI: Still TBD

# Wrapup
## Wrapup
- Thank you!
- Questions?
- Get the deck [stephlocke.info/Rtraining](http://stephlocke.info/Rtraining)
- Follow up [T: SteffLocke](https://twitter.com/stefflocke)
