---
title: 'Skilling up to code with data'
author: "Steph Locke (@SteffLocke)"
date: '`r Sys.Date()`'
output:
  Rtraining::stephRevealSlideStyle
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r autodoc, child='../../generics/AboutMe.Rmd', eval=TRUE}
```

# Agenda
## Agenda
- Why code with data
- What coding languages can be used
- Coding best practices
- Source control
- Testing
- Continuous testing (& deployment)
- Coding your infrastructure
- Wrap up

```{r autodoc, child='subDocs/whycodewithdata.Rmd', eval=TRUE}
```

```{r autodoc, child='subDocs/whatcodinglanguages.Rmd', eval=TRUE}
```

```{r autodoc, child='subDocs/codingbestpractices.Rmd', eval=TRUE}
```

```{r autodoc, child='subDocs/sourcecontrol.Rmd', eval=TRUE}
```

```{r autodoc, child='subDocs/testing.Rmd', eval=TRUE}
```

```{r autodoc, child='subDocs/ci.Rmd', eval=TRUE}
```

```{r autodoc, child='subDocs/codedinfrastructure.Rmd', eval=TRUE}
```

# Conclusion
## Why code?
>- To save time
>- To be right and know it
>- To be replacable

## What to code?
From databases to reports, you can code it!

## How best to do it?
>- KISS
>- Test, test, test

## Where to go from here?
>- Get this online & use the various links
>- Get started!
>- Keep in touch: @SteffLocke
