---
title: "Knowing your Rs from your elbow"
author: "Steph Locke"
date: "`r Sys.Date()`"
output:
  beamer_presentation:
    template: main2.tex
    theme: m
    pandoc_args: [
      "--latex-engine=xelatex"
    ]
---

## Steph Locke | Not my Rs

- Star of presentations such as "the LaTeX show"!
- Local user group leader
- blog: [itsalocke.com](http://itsalocke.com)
- t: [\@stefflocke](http://twitter.com/stefflocke)

## What's this about Rs?
- R is an open source language, made out of the ashes of S
- It started off stats
- Now has excellent graphics, .js, & doc facilities

## Why should you know your Rs from your elbow?
- Markdown!
- Interactive data viz via js libraries
- Fully CI/CD capable
- Tons of non-web uses
- Easier payloads from analytical teams

## What does R look like? | Basics
```{r}
#Define a variable
a<-25

#Call a variable
a

#Do something to it
a+1
```

## What does R look like? | Functions
```{r}
#Define a function
inflateAudienceFigs<-function(x) x*100

#Call a function
inflateAudienceFigs(a)
```

## What does R look like? | Extensions
```{r, eval=FALSE }
#Get a package
install.packages("commonmark")

#Activate a package
library(commonmark)
```


## What does R look like? | OO
```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
library("R6")
```

```{r}
# Orig OO (s3): cyclismo.org/tutorial/R/s3Classes.html
library(R6)
Loan<-R6Class("Loan", 
              public=list(term=NA
                         ,initialize=function(term){
                           if(!missing(term)){ 
                              self$term<-term 
                              }} 
                         ,extendBy=function(ext){ 
                            self$term<-self$term+ext
                            }))
```

## What does R look like? | OO
```{r}
acc<-Loan$new(36)
acc$extendBy(6)
acc$term
```

## What does R look like? | Piping
```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
library(magrittr)
```

```{r, results='hide', eval=FALSE}
library(magrittr)

#Typical
pairs(iris)

#Pipe
iris %>% pairs
iris %>% tail(.) %>% pairs
iris %>% {tail(.,nrow(.)/5)} %>% pairs
```

## Let's do some JS stuff!