---
title: 'Shiny: dashboards in R'
author: "Steph Locke"
date: "Wednesday, February 18, 2015"
runtime: shiny
output:
  ioslides_presentation:
    css: Look.css
---


## First - R {.build}
Who's using R already?

I'll be covering off a reasonable amount of code as I go but check out my [R Intro]() for a more thorough overview.

## Second - What is Shiny?

- An interactive report framework
- An R package that is available free (as is the server edition)
- Uses of "modern web standards" like bootstrap under the hood 

## Third
```{r, echo = FALSE}
library(shiny)
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height="75%"
  )
)
```

## Housekeeping
- Approx 55 mins talk + 20 mins Q&A!
- Ask your questions throughout

```{r autodoc, child='../presentationguff/Scenario.Rmd', eval=TRUE}
```

```{r autodoc, child='Objective.Rmd', eval=TRUE}
```


## Recommended reading
- [Shiny homepage](http://shiny.rstudio.com/)
- A bit outdated but: [Web Application Development with R Using Shiny](http://www.amazon.co.uk/gp/product/B00G395OOY)

```{r autodoc, child='../presentationguff/AboutMe.Rmd', eval=TRUE}
```

