---
title: "R 101"
author: "Steph Locke"
date: "`r Sys.Date()`"
output:
  beamer_presentation:
    template: default.tex
    theme: m
    pandoc_args: [
      "--latex-engine=xelatex"
    ]
---

## Steph Locke | Who I am

- Credit Risk & BI specialist
- Soon to be consultant with Mango Solutions
- Owner of a BA in Philosophy
- github: [stephlocke/Rtraining](http://github.com/stephlocke/Rtraining)
- blog: [itsalocke.com](http://itsalocke.com)
- t: [\@stefflocke](http://twitter.com/stefflocke)

# R

## R | A brief history
- S, born 1976 in Bell Laboratories
- R, born 1997 in a uni in NZ
- R Foundation, born 2002
- R Consortium, born 2015
- R now ranked 6th most popular language by IEEE

## R | Why use it?
- For the stats
- For the reproducibility
- For the time it can save
- For the flexibility
- For the money

## R | Why not Python?
Firstly, Python is a valid way to go. There are number of really good libraries out there for number crunching etc. and it is a well written language with few "quirks"

Secondly, why R is my preference:

- Easy install
- Strong community base
- Data focused
- Very flexible and extendable
- It's the favourite to win

But... "production" code is probably better in Python 

# R funadamentals
## What does R look like? | Basics
```{r}
# Define a variable
a=25
a<-25

# Call a variable
a

# Do something to it
a+1
```

## What does R look like? | Data types
```{r}
# Numeric
25

# Character
"25"

# Factor
a = factor("25")
as.numeric(a)
as.character(a)
```

## What does R look like? | Constructs p1
```{r}
# Vector
a<-c(25, 30)

# Matrix
matrix(a)
```

## What does R look like? | Constructs p2
```{r}
# Data frame
data.frame(a,b=a/5,c=LETTERS[1:2])

# List
list(vector=a, matrix=matrix(a))
```


## What does R look like? | Functions
```{r}
# Define a function
showAsPercent<-function(x) {
  paste0(round(x*100 ,0) ,"%")
}

# Call a function
showAsPercent(0.1)
```

## What does R look like? | Extensions
```{r, eval=FALSE }
# Get a package
install.packages("caret")

# Activate a package
library(caret)
```

<!--
## What does R look like? | OO
```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
library("R6")
```

```{r}
# Orig OO (s3): cyclismo.org/tutorial/R/s3Classes.html
library(R6)
Loan<-R6Class("Loan", 
              public=list(term=NA
                         ,initialize=function(term){
                           if(!missing(term)){ 
                              self$term<-term 
                              }} 
                         ,extendBy=function(ext){ 
                            self$term<-self$term+ext
                            }))
```

## What does R look like? | OO
```{r}
acc<-Loan$new(36)
acc$extendBy(6)
acc$term
```
-->
## What does R look like? | Piping
```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
library(magrittr)
```

```{r, results='hide', eval=FALSE}
library(magrittr)

#Typical
pairs(iris)

#Pipe
iris %>% pairs
iris %>% tail(.) %>% pairs
iris %>% {tail(.,nrow(.)/5)} %>% pairs
```

# Next steps
## Find out more

### Online
- Modern R [DataCamp](http://datacamp.com) 
- Statistics R [Coursera](https://www.coursera.org/specialization/jhudatascience) 
- [R-bloggers](http://www.r-bloggers.com/) 
- [Advanced R programming](http://adv-r.had.co.nz/)
- [Writing R packages](http://r-pkgs.had.co.nz/)


### In-person
- R user groups e.g. [CaRdiff](http://meetup.com/cardiff-r-user-group)
- Conferences e.g. [EARL](http://www.earl-conference.com/), [SQL Relay](http://sqlrelay.co.uk)


## Get this presentation
This presentation is available on [github.com/stephlocke/Rtraining](https://github.com/stephlocke/Rtraining). All the code is available for you to take a copy and play with to help you learn on the go.

If you have any questions, contact me! 

[itsalocke.com](http://itsalocke.com) | [github.com/StephLocke](https://github.com/StephLocke) | [\@SteffLocke](https://twitter.com/stefflocke)