  # Problemset Example

    Example of an RTutor interactive Problemset
    Author:  Sebastian Kranz
    Date:    12.06.2014

    Adapt the working directory below and press Ctrl-Alt-R (run all chunks).
    This creates the problem set files and the sample solution from this solution file.

    #< ignore
    ```{r " "}
    library(RTutor)
    #library(restorepoint)
    if(!exists("exerciselocation")) {
      exerciselocation<- if (interactive()) {
        choose.dir(getwd(), "Choose a suitable folder")
        }else{
          "."
        }
    }
    setwd(exerciselocation)
    ps.name = "example"; sol.file = paste0(ps.name,"_sol.Rmd")
    libs = NULL # character vector of all packages you load in the problem set
    #name.rmd.chunks(sol.file) # set auto chunk names in this file
    create.ps(sol.file=sol.file, ps.name=ps.name, user.name=NULL,
              libs=libs, extra.code.file=NULL, var.txt.file=NULL)

    # When you want to solve in the browser
    show.ps(ps.name,launch.browser=TRUE, load.sav=FALSE,
            sample.solution=FALSE, is.solved=FALSE)

    ```
    #>

    ## Exercise 1 -- Summary statistics

    a) We often want to compute some summary statistic of a vector.
    For example:
    ```{r "1 a)"}
    #< task_notest
    x = 10:20
    # Computing the sum of x
    sum(x)
    #>
    ```

    Now compute the mean of x.
    ```{r "1 a) 2"}
    mean(x)
    #< hint
    display("There already exist R functions for many things. To find them use Google, e.g. search for 'R compute mean'.")
    #>
    ```

    #< award "mean means mean"
    Well, in some occasions one can just guess the name of an R function.
    The function to compute the mean of a vector, or matrix is called 'mean'.
    Usually, it is much quicker to goggle than to guess function names, however.
    #>


    ## Exercise 2 -- Computing with vectors
    ```{r "2 "}
    #< settings
    import.var = c("x")
    #>
    ```
    a) Let y be a vector that contains the squared elements of x. Show y
    ```{r "2 a)"}
    y = x^2
    y
    ```

    #< info "random numbers"
    Here are examples for generating random numbers
    ```{r "1 "}
    runif(3,0,100)
    sample(1:100,5)
    ```
    #>